Uncertain Effects of DFT Functionals on Time-of-flight Calculations of Organic semiconductor

### 2024-09-17 paper.tex
edit

\usepackage{units}
\usepackage{lineno}
%++++++++++++++++++++++++++++++++++++++++

\begin{document}
\linenumbers
\title{Uncertain Effects of DFT Functionals on Time-of-flight Calculations of Organic semiconductor }
\author{authors}
\date{\today}
\maketitle

\begin{abstract}
In this paper, the time-of-flight (ToF) is used to quantify the charge mobility in OSC. 
Using ToF as the quantity of interest, the uncertainty effect of the DFT functionals on the ToF in a BCP device is studied. 
Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the ToF can have a relatively large deviation.
Further investigation reveals that ToF can be sensitive to the energy of a single molecule, leading to the ToF being sensitive to DFT functionals.

@@

\section{Introduction}
Random walk in random environments is often used to model physical processes taking into account the varying disorder levels and environmental factors that influence the walker's movement. 
These disorders and environmental factors can introduce a level of uncertainty that significantly impacts the overall rates of the random walk, ultimately affecting the quantities of interest one aims to obtain.

A specific type of random walk in random environments is the charge transport in organic semiconductors (OSC), which consists of the amorphous mesoscopic structure due to spatially disordered molecular arrangement. 
Such structural disorder translates into electronic structure disorder, including energy disorder and coupling element disorder, which eventually leads the charge transport processes to be modeled as continuous time random walks (CTRWs). By representing the molecule as vertexes, the edge weights are assigned as the transition rates between the corresponding molecules, and the charge carriers are random walkers. 
The uncertainty brought by electronic structure disorder and environmental factors is reflected in the transition rates, that is the edge weights of the CTRWs.

While the transition rates in those CTRWs can be calculated in a first-principle multiscale approach, this method involves some level of approximations. 
Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential in providing a time-series behavior of the charge dynamics. 
But due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT). DFT has two challenges. Firstly, it is computationally impossible to perform electronic structure calculations for the whole OSC device. And secondly, the exchange-correlation potential in DFT has an unknown formula.

The first challenge is overcome by approximating the electron dynamics as transition processes between the localized states, with the transition rates calculated as the temperature-activated bi-molecule transition rates, known as the Marcus rate. 
The second challenge is addressed by utilizing DFT functionals to represent the exchange-correlation potential. 
While there are benchmark results concerning the molecular energy calculation using different DFT functionals as well as rich literature on charge transport in the multiscale model OSC, a quantitative study of DFT functionals' effect on the charge transport processes is missing. 
Also missing is the influence of the uncertainty in the electronic structure properties on the quantity of interest.

There are many challenges for this investigation. Firstly, due to the number of molecules ($\sim 1000$), since the CTRWs are usually of high dimensions, quantifying uncertainty in such high dimensions is numerically challenging. Secondly, simulating the CTRWs process itself can be a computationally challenging task due to some convergence issues.
Last but not least, the exact DFT functionals are not known so as the distribution of the transition rates for any two specific molecules.

One of the main quantities of interest to characterize the charge transport in OSC is charge mobility. Using this as the quantity of interest,
the goal of this work is to investigate how the DFT functionals affect the electronic structures and charge mobility. The uncertainty due to the environmental factors that cause a change in the molecules' position is not considered in this work, although this topic itself is very important.
We want to answer the following questions: 
\begin{itemize}
    \item How do DFT functionals change the reorganization energy, distribution of molecule energies and coupling elements? 
    \item How do DFT functionals change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) has the most impact on the uncertainty of charge mobility?
    \item Can we estimate the range of the quantity of interest, given a confidence level?
\end{itemize}

With an external electric field, the charge mobility can be calculated as $\mu = \frac{\vec{v} \vec{F}}{|\vec{F}|^2}$ where $\vec{v}$ is the average drift-diffusive velocity of the charge carrier(s).
Without an electric field, $\vec{v}$ is the purely diffusive velocity. 
In electronic devices, the velocity is obtained from \textit{time-of-flight} (ToF) experiments, where charge carriers are injected into the cathode and collected at the anode. The ToF, denoted as $\tau$, is the period from injection to detection of at least one charge carrier. 
Then the velocity is simply $|\vec{v}| = \frac{L}{\tau}$, where $L$ is the length of the sample, which is usually chosen to be along the electric field direction if there is any.

Analogously, the ToF calculation for multiscale modeled OSC sets up some molecules as \textit{Source} and some as \textit{Sink}. The key quantity for characterizing the charge transport, especially for uncertainty quantification, is the ToF, since the sample length $L$ is fixed and can be seen as a constant.

In literature regarding multiscale modeled OSC, most works on charge transport reported steady-state charge mobility. This setting repeats the molecule graph infinitely in all three dimensions by periodic boundary conditions. Then, the CTRWs on the graph are simulated, usually by kinetic Monte Carlo numerically. However, this method suffers from challenges such as convergence issues. Namely, there is no guarantee that the number of Monte Carlo simulations will correctly present the charge carrier occupation in each molecule, and this becomes a problem if we want to calculate some quantities for a confidence level.

Therefore, the charge mobility based on ToF is the focus to characterize charge transport.
Specifically, diffusive ToF with one charge carrier is used as the quantities of interest, and its calculation is based on the hitting time of a continuous time Markov chain. 
Diffusive ToF only considers electronic structures, without the influence of external electric fields, making clear the sensitivity effect path starting from DFT functional to electronic structures and eventually to ToF mobility. 
We only consider the CTRWs with one charge carrier, since multiple charge carriers will lead to a huge dimension, making the uncertainty quantification difficult to approach computationally, plus other issues. Also, since we only simulate a very limited-size system, using only one charge carrier is aligned with the low carrier density at the electric device level. 
Furthermore, multiple charge carriers will effectively disable some low-energy molecules which are important in uncertainty quantification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiscale Model}
\label{sec:MSM}
To perform multiscale modeling, the BCP (dimethyl-diphenyl-1,10-phenanthroline) device is used as the OSC in this work, since BCP has small conductivity and has been used as hole-trapping materials \cite{tsung_carrier_2008}.
A BCP device consisting of 1000 molecules is shown in Fig.\ref{fig:ToFFill}(b) with atomistic details.

%\begin{figure}
%    \centering
%    \includegraphics[width=0.4\textwidth]{figs/BCP_trap.png}
%   \caption{ BCP device simulated from MD. The Source and Sink molecules are highlighted by the blue color, and the molecule corresponding to node 66 is highlighted by the red color. The other BCP molecules are in grey. }
%   \label{fig:BCP}
%\end{figure}

The atomistic coordinates as well as the center-of-mass (COM) of each BCP molecule are generated from atomistic Molecular dynamics simulation, whose details are given in the Appendix.
For modeling purposes, this molecular system is modeled as a graph on which the random walk takes place. Each vertice represents a molecule, which also corresponds to a localized state mentioned in the introduction. 
Using a cutoff distance $r_\text{cutoff}$, any two molecules whose COM is within $r_\text{cutoff}=0.5$ [nm] are connected by directed edges with a weight $\omega_{i,j}$, and usually $\omega_{i,j} \neq \omega_{j,i}$.
The directed edge weights $\omega_{i,j}$ takes the electron transfer rate from localized state of molecule $i$ to that of molecule $j$, commonly expressed as Marcus rate:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant, $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation. The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated cyclic boundary conditions depending on the boundary condition.
The remaining quantities are calculated for each molecule using principles from quantum mechanics and classical mechanics: the reorganization energy $\lambda_{i,j}$, the electronic coupling $J_{ij}$, and the energy difference $\Delta E_{i,j} = E_i - E_j$ (all in \unit[]{eV}).

In summary, the multiscale model for ToF calculation refers to the process: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined,
secondly, quantum electronic structure calculation is performed to obtain the parameter sets $\left\{\lambda_{i,j}\right\}$,  $\left\{J_{ij}\right\}$, and $\left\{\Delta E_{i,j}\right\}$ based on the atomistic details to define the edge weights. Finally from those parameters, ToF is evaluated.
In the remaining section, we will introduce the calculation details of $\left\{\lambda_{i,j}\right\}$,  $\left\{J_{ij}\right\}$, $\left\{\Delta E_{i,j}\right\}$ and ToF.

\subsection{Electronic Structure Calculation} 
Each molecule is an $N_\text{el}$-electron system, and in quantum mechanics, the probability of finding electrons in space is described by the wavefunction.
The energy eigenvalue from the standard Kohn–Sham model \cite{kohn_self_1965} for a molecule (consisting of electrons and nuclei) reads:
\begin{equation}
    E_0 = \text{inf}\{ E^\text{KS}(\psi),\psi=(\phi_1,\cdots,\phi_{N_\text{el}}) \in (L_2(\mathbb{R}^3))^N, \int_{\mathbb{R}^3} \phi_i \phi_j =\delta_{ij} \} 
    \label{eq:KS_model}
\end{equation}
where the single-electron wavefunction $\phi_i$ satisfies $(-\frac{1}{2}\nabla^2_\mathbf{r} + \hat{V}_\text{ext} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}) \phi_i^\text{KS} =  E^\text{KS}_i[\rho] \phi^\text{KS}_i$ with electron density $\rho$. 
The kinetic energy operator is $-\frac{1}{2}\nabla^2_\mathbf{r}$, external potential energy operator $\hat{V}_\text{ext}$ includes all electrostatic background potentials such as the nuclear potential of all the atoms.
The Coulomb interaction operator is $\hat{V}_\text{H}[\rho] = \int_{\mathbb{R}^3} \frac{\rho(\vec{r}')}{ |\vec{r} - \vec{r}'| }$, and Kohn-Sham energy $E^\text{KS}_i$ of electron $i$. The molecule wavefunction $\psi$ lives in squared integrable Lebesgue space $L_2(\mathbb{R}^3)$.

The exchange-correlation operator $\hat{V}_\text{XC}$ accounts for all the nonclassical terms, namely, the potential and kinetic energy associated with electron exchange and correlation. Knowledge of the exact $\hat{V}_\text{XC}$ makes obtaining the exact energy eigenvalue of many-body ground state possible. However, the exact $\hat{V}_\text{XC}$ is unknown and approximations, such as local density approximation (LDA), generalized gradient approximation (GGA) or a mixture of those two approximations with other models, are used in practice as the form of DFT functionals. 
The ten DFT functionals are shown in Table \ref{tab:para}.

The energy eigenvalue $E_0$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $E_0$.
The reorganization energy $\lambda_{i,j}$ from molecule $i$ to molecule $j$ is given as:
\begin{equation}
    \lambda_{ij} = E_i^\text{nC} - E_i^\text{nN} + E_j^\text{cN} - E_j^\text{cC}
\end{equation}
where $E_i^\text{nC}$ is the energy eigenvalue of the neutral molecule $i$ with the optimized geometry of charged molecule. When charge carriers are holes, a charged molecule has one electron less compared to a neutral molecule. Similarly, $E_j^\text{cN}$ is the energy eigenvalue of the charged molecule with the optimized geometry of the neutral molecule. For the BCP device, we obtain $\lambda_{ij}=0.50$ eV since this is only one type of molecule.

The site energy $E_i$ is calculated by:
\begin{equation}
    E_i = (E_i^\text{cC} - E_i^\text{nN}) + E_i^\text{el}
    \label{eq:siteE}
\end{equation}
where $E_i^\text{nN}$ is single-point energy of the neutral molecule $i$ with the optimized geometry of neutral molecule. Similarly, $E_i^\text{cC}$ is the single-point energy of the charged molecule $i$ with the optimized geometry of the charged molecule. In physical interpretation, $E_i^\text{cC} - E_i^\text{nN}$ is the adiabatic ionization potential of molecule $i$.
And $E_i^\text{el}$ is the electrostatic interactions given by:
%
\begin{equation}
    E_i^\text{el} = \frac{1}{4 \pi \epsilon_0} \sum\limits_{a_i} \sum\limits_{b_k,k\neq i} 
    \frac{(q_{a_i}^\text{c} - q_{a_i}^\text{n}) q_{b_k}^\text{n}}{\epsilon_s r_{a_i,b_k}}
    \label{equ:Eel}
\end{equation}
%
where $i,k$ index molecules, $a_i$ and $b_k$ refer to atoms belonging to molecule $i,k$, $r_{a_i,b_k} = || \vec{r}_{a_i} - \vec{r}_{b_k} ||_2$ is the distance between atoms $a_i$ and $b_k$, and $\epsilon_s$ represents the static relative dielectric constant and is a function of the dipole moment of the molecule. From the atomic charges, the dipole moment is calculated via $\mu_i = \sum\limits_{a_i} q_{a_i} \cdot \vec{r}_{a_i}$. The molecule energies and their distribution are shown in the appendix.

%%%%%%%
The coupling element $J_{i,j}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
\begin{equation}
    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)\mathbf{S}_{i,j} }{ 1- \mathbf{S}_{i,j}^2 }
    \label{equ:JAB}
\end{equation}
where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $\mathbf{S}_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$. A single molecule is called a monomer, and a pair of two molecules is called a dimer.

Denote $\psi^\text{D}$ as the electron wave function of the two molecules,  $J^0_{i,j}$ can be calculated via:
$
    J^0_{i,j} = \mathbf{\gamma}^i \text{diag}(\mathcal{E}) \mathbf{\gamma}^j
$, 
where $\mathbf{\gamma}^i = \langle \psi^i | \psi^\text{D} \rangle$ and $\mathbf{\gamma}^j = \langle \psi^j | \psi^\text{D} \rangle$ are called the projections of the monomer orbitals $\psi^i, \psi^j$ on the dimer orbitals $\psi^\text{D}$. And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting of energy eigenvalues of the one-particle wave function of the dimer. The molecular coupling element distribution is shown in the appendix.

\section{Time-of-flight Calculation}
After defining the graph $\mathbf{G}=(\mathbf{W},\mathbf{E})$ and calculating the edge weights from the multiscale model, the charge dynamics can be modeled as a continuous-time random walk process on the graph. 
One of the quantity of interest in charge transport is the Time-of-flight from Source to Sink. 
To model the Source-Sink conditions in many devices such as the neuromorphic devices mentioned in the introduction, some vertices are used as \textbf{Source} to represent the electrode where charge carriers are injected, and some vertices as \textbf{Sink} where charge carriers are detected and ToF recorded.
Due to Coulomb repulsion, each node can be occupied by one charge carrier at most, so a system with $N$ molecules and $N_c$ charge carriers has a total of $C^N_{N_C}$ occupation situations. Each of these occupation situations is considered as a state $\mathbf{s}$. 
If all the carriers' occupations are in the Source node, the state is called the Source state, and if at least one of the Sink nodes is occupied, the state is called the Sink state. 
The transition rates between the states can be obtained from the adjacency matrix $\mathbf{W}:\omega_{i,j}$, since the connectivity of states is encoded in the connectivity of the nodes, as detailed in ~\cite{chen_graph_2024}. 
According to such connectivity, 
the transition rates $\Omega_{\mathbf{s} \mathbf{s}' }$ from state $\mathbf{s}$ to $\mathbf{s}'$ is:
\begin{equation}\label{eq:transition_rates}
	\Omega_{\mathbf{s} \mathbf{s}^\prime} =
	\begin{cases}
	     0			&  \mathbf{s} \text{ is not connected to } \mathbf{s}^\prime,\\
	    \omega_{ij}	&  \mathbf{s} \text{ is connected to } \mathbf{s}^\prime \text{ due to } (i,j)
	\end{cases}
\end{equation}

>>>>

\usepackage{units}
\usepackage{lineno}
\usepackage{comment}
\usepackage{float}
%++++++++++++++++++++++++++++++++++++++++

\begin{document}
\linenumbers
\title{Uncertain Effects of DFT Functionals on Time-of-flight Calculations of Organic semiconductor }
\author{authors}
\date{\today}
\maketitle
\begin{abstract}
In this paper, the time-of-flight (ToF) is used to quantify the charge mobility in OSC. 
Using ToF as the quantity of interest, the uncertainty effect of the DFT functionals on the ToF in a BCP device is studied. 
Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the ToF can have a relatively large deviation.
Further investigation reveals that ToF can be sensitive to the energy of a single molecule, leading to the ToF being sensitive to DFT functionals.

@@

\section{Introduction}
Random walks in random environments (RWRE) are widely used to model physical processes, incorporating the varying levels of disorder and environmental factors that influence movement. 
These disorders and environmental factors can introduce a level of uncertainty that significantly impacts the overall rates of the random walk, ultimately affecting the quantities of interest one aims to obtain.

A notable example of RWRE is charge transport in organic semiconductors (OSCs), characterized by an amorphous mesoscopic structure due to spatially disordered molecular arrangements. 
This structural disorder translates into electronic structure disorder, including energy disorder and coupling element disorder, leading to the modeling of charge transport processes as continuous time random walks (CTRWs) on a graph. 
Specifically, the molecules can be represented as nodes in a graph, the transition rates between them (edge weights) correspond to the transition rates between the molecules, and the charge carriers become the random walkers. The details of specifying the graph will be introduced in the Section 2. The uncertainty from electronic structure disorder and environmental factors is reflected in these transition rates.

While the transition rates in those CTRWs can be calculated in a first-principle multiscale approach, but it involves some level of approximations. 
Since the charge transport in OSC involves electrons, quantum mechanics and Schr\"odinger equation are essential in providing a time-series behavior of the charge dynamics. 
But due to the complexity of Schr\"odinger Equation, one alternative theory is the density functional theory (DFT). 
DFT faces two main challenges: it is computationally impractical for entire OSC devices and the exchange-correlation potential lacks an explicit formula.

The first challenge is mitigated by approximating electron dynamics as transition processes between localized states which contain most of the molecular electron, with transition rates calculated using the temperature-activated bi-molecular Marcus rate. 
The second challenge is addressed by employing DFT functionals to approximate the exchange-correlation potential. 
Despite benchmark results on molecular energy calculations with various DFT functionals and extensive literature on charge transport in multiscale models of OSCs, there is a lack of quantitative studies on how DFT functionals affect charge transport processes, and the influence of uncertainty in electronic structure properties.

Several challenges arise in this investigation. The high dimensionality of CTRWs (due to the large number of molecules, typically around 1000) makes uncertainty quantification numerically challenging. Secondly, simulating CTRWs is also computationally demanding due to convergence issues. Additionally, the exact DFT exchange-correlation functional and the distribution of transition rates for specific molecules are unknown.

One of the main quantities of interest to characterize the charge transport in OSC is charge mobility. Using this as the quantity of interest,
the goal of this work is to investigate how the DFT functionals affect the electronic structures and charge mobility. The uncertainty due to the environmental factors that cause a change in the molecules' position is not considered in this work, although this topic deserves intensive studies.
We want to focus on the following questions: 
\begin{itemize}
    \item How do DFT functionals change the reorganization energy, distribution of molecule energies and coupling elements? 
    \item How do DFT functionals change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) has the most impact on the uncertainty of charge mobility?
    \item Can we estimate the range of the quantity of interest, given a confidence level?
\end{itemize}

Charge mobility, in the presence of an external electric field, can be calculated as $\mu = \frac{\vec{v} \cdot \vec{F}}{|\vec{F}|^2}$, where $\vec{v}$ is the average drift-diffusive velocity of the charge carrier(s). Without an electric field, $\vec{v}$ is the purely diffusive velocity. In electronic devices, velocity is obtained from time-of-flight (ToF) experiments, where charge carriers are injected into the cathode and collected at the anode. The ToF, denoted as $\tau$, is the period from injection to detection of at least one charge carrier. The velocity is given by $|\vec{v}| = \frac{L}{\tau}$, where $L$ is the sample length, usually aligned with the electric field direction if present.

For multiscale modeled OSCs, ToF calculations involve setting some molecules as \textit{Source} and some as \textit{Sink}. The key quantity for characterizing charge transport, especially for uncertainty quantification, is ToF, as the sample length $L$ is fixed and constant.

Most literature on charge transport in multiscale modeled OSCs reports steady-state charge mobility, using periodic boundary conditions to simulate CTRWs on an infinitely repeating molecular graph, typically via kinetic Monte Carlo simulations. However, this method faces challenges, particularly convergence issues, which complicate the accurate calculation of quantities with a desired confidence level.

Therefore, this work focuses on characterizing charge mobility based on ToF, specifically diffusive ToF with a single charge carrier, calculated from the hitting time of a continuous time Markov chain. This approach excludes the effects of external electric fields, clarifying the sensitivity from DFT functional to electronic structures and ToF mobility. 
Furthermore, considering only one charge carrier aligns with the low carrier density in electronic devices and avoids the computational complexity of simulating multiple charge carriers, which can obscure important low-energy molecules in uncertainty quantification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiscale Model}
\label{sec:MSM}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MSM.png}
    \caption{The multiscale model workflow for OSC. Step 1: MD simulation to generate atom coordinates. Step 2: Molecule energy $E_i$ calculation. Step 3: Calculation of Reorganization energy $\lambda_{i,j}$ and coupling element $J_{i,j}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$. Step 4: Modelling dynamics on device level, such as ToF calculation.}
    \label{fig:MSM}
\end{figure}

Figure \ref{fig:scatterE} shows the workflow of the multiscale model for ToF calculation. In brief summary, the process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates from which the vertex and edge sets are defined.
Specifically, using a cutoff distance $r_\text{cutoff}$, any two molecules whose center of mass (COM) within $r_\text{cutoff}=0.5$ [nm] form a pair of molecules where directed edge weight can be calculated.
Secondly, quantum electronic structure calculation is performed to obtain the electronic structure properties: The molecule energy $E_i$ of molecule $i$, the reorganization energy between $\left\{\lambda_{i,j}\right\}$ and coupling element $\left\{\Delta J_{i,j}\right\}$ between the pair of molecules $i$ and $j$. All in unit of eV.

Then, those electronic structure properties are used to calculate the bi-molecular Marcus rate between the molecules:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{i,j}|^2}{\sqrt{4\pi \lambda_{i,j} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{i,j} + q \vec{F} \cdot \vec{r}_{i,j} - \lambda_{i,j})^2}{4\lambda_{i,j} k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant, $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), external electric field $\vec{F}$ and the charge of the carrier $q$ (in \unit[]{e}) can be considered as parameters of the simulation. The vector $\vec{r}_{i,j} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses of molecules $i$ and $j$, which is calculated using cyclic boundary conditions depending on system setting. And $\Delta E_{i,j} = E_i - E_j$ is the energy difference between a pair of molecules.
Finally, the quantity of interest, such as ToF $\tau$, can be calculated from the transition rates $\omega_{ij}$.

\subsection{Molecule Dynamics Simulation}
In a material system of $N_a$ atoms with mass and position denoted by $m_i$ and $\vec{r}_i$ respectively, molecular dynamics (MD) models the evolution of the atomic coordinate using Newton's second law, which is written in Hamilton equation: 
\begin{equation}
    \begin{cases}
        \frac{d \vec{r}_i}{dt} = \frac{\partial H }{\partial \vec{p}_i} \\
        \frac{d \vec{p}_i}{dt} = -\frac{\partial H }{\partial \vec{r}_i}
    \end{cases}
    \label{eq:Hamilton}
\end{equation}
for $i=1,\cdots,N_a$, where the Hamiltonian $H$ reads:
\begin{equation}
    H=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})
    \label{eq:Hamilton2}
\end{equation}

In principle the potential energy function $U(\vec{r}_1,\cdots,\vec{r}_{N_a})$ of the system can be obtained from electronic structure models. In practice, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
In our work, constant the molecule number $N=1000$, a temperature $T=300$ K and a pressure at 1 atm is used to achieve an NPT ensemble. 
One of the final BCP morphology is chosen as OSC for charge transport study.

\subsection{Electronic Structure Calculation} 
The molecule energy $E_i$ in the multiscale model is calculated as:
\begin{equation}
E_i = (U^\text{cC}_i - U^\text{nN}_i) + (E^\text{c}_i - E^\text{n}_i)
\label{eq:E_i}
\end{equation}
where $U^\text{cC}_i$ is the internal energy of charged molecule $i$ in the optimized charged geometry, and $U^\text{nN}_i$ is the internal energy of neutral molecule $i$ in the optimized neutral geometry. The calculation of $U$ and how to obtain optimized geometry will be introduced in the subsection DFT Calculation.
In the superscript the lowercase letter "c/n" represents the molecule state of being charged/neutral and uppercase letter "C/N" represents the geometry of the charged/neutral molecule. This notation also applies for $E^\text{c}_i$, $E^\text{n}_i$. 
And $E^\text{n}_i = E^\text{n,el}_i + E^\text{n,induce}_i$ is the energy due to the electrostatic and induced dipole moment effect. Compared with the electrostatic energy calculated using the dielectric constant, this energy in multiscale model is very sensitive to the molecule structure, making the uncertainty quantification of charge transport in multiscale model much more important. 
A precise method for calculating $E^\text{n}_i$ is to use the Thole Model as detailed in \cite{Baumeier2011}.

This method has the steps include: first, each atom $a_i$ is initialized with charges $q_{a_i}$ and dipole moment $D_{a_i}$. 
Then the induced dipoles of each atom are calculated using the electric field generated by other atoms $b_j$.
This calculation continuous iteratively to update the induced dipoles of every atom by considering the fields due to other dipoles.
Finally, it checks for convergence, if the induced dipoles have not changed significantly from one iteration to the next, the iterative process stops.
Finally, the electrostatic energy and polarization energy using the final set of induced dipoles and atomic charges. So in summary, $E^\text{n}_i$ is a function of all atoms' charges and induced dipoles: $E^\text{n}_i = \sum\limits_{a_i} f(q_{a_i}, D_{a_i})$.

The reorganization energy $\lambda_{i,j}$ between molecule $i$ to molecule $j$ is given as:
\begin{equation}
    \lambda_{ij} = U_i^\text{nC} - U_i^\text{nN} + U_j^\text{cN} - U_j^\text{cC}
\end{equation}

%%%%%%%
The coupling element $J_{i,j}$ between molecule $i$ and $j$ is calculated \cite{baumeier_density_2010} using the electron wave function of the molecules obtained from the Kohn-Sham equation: 
\begin{equation}
    J_{i,j} = \frac{ J^0_{i,j}- \frac{1}{2}(e_i+e_j)S_{i,j} }{ 1- S_{i,j}^2 }
    \label{equ:JAB}
\end{equation}
where $J^0_{i,j} = \langle \psi^i | \hat{H} | \psi^j \rangle $, $e_i = \langle \psi^i | \hat{H} | \psi^i \rangle $, $e_j = \langle \psi^j | \hat{H} | \psi^j \rangle $, and $S_{i,j}=\langle \psi^i | \psi^j \rangle $ with bra-ket notation, $\hat{H}$ is the Hamiltonian of the electron wave function, and $\psi^{i,(j)}$ is the electron wave function of molecule $i(j)$. A single molecule is called a monomer, and a pair of two molecules is called a dimer.

Denote $\psi^\text{D}$ as the electron wave function of the two molecules,  $J^0_{i,j}$ can be calculated via:
$
    J^0_{i,j} = \mathbf{\gamma}^i \text{diag}(\mathcal{E}) \mathbf{\gamma}^j
$, 
where $\mathbf{\gamma}^i = \langle \psi^i | \psi^\text{D} \rangle$ and $\mathbf{\gamma}^j = \langle \psi^j | \psi^\text{D} \rangle$ are called the projections of the monomer orbitals $\psi^i, \psi^j$ on the dimer orbitals $\psi^\text{D}$. And $\text{diag}(\mathcal{E})$ is the diagonal matrix consisting of energy eigenvalues of the one-particle wave function of the dimer.

In conclusion, the calculation of electronic structure relies on the internal energy and electron wave function. As mentioned in the introduction, DFT is used to calculate these two quantities. The next subsection will introduce the details of DFT.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{DFT Calculation}
In multiscale model, each molecule is an $N_\text{el}$-electron system, and the probability of finding electrons in space is described by the wavefunction.
In DFT, the internal energy calculated from the Kohn–Sham equation \cite{kohn_self_1965} reads:

\begin{equation}
    U^\text{KS}[\rho] = T_s[\rho] + \int \hat{V}_\text{ext}(\vec{r}) \rho(\vec{r}) d \vec{r} + \hat{V}_\text{H}[\rho] + \hat{V}_\text{XC}[\rho]
    \label{eq:KS_model}
\end{equation}
where the electron density is $\rho=\sum\limits_{i=1}^{N_\text{el}} \phi_i^\star(\vec{r}) \phi_i(\vec{r})$, $T_s[\rho]$ is the kinetic energy depending on $\rho$,  $\hat{V}_\text{ext}$ is the external potential energy,  $\hat{V}_\text{H}[\rho]$ is the Hartree energy accounting for the Coulomb interaction, $\hat{V}_\text{XC}[\rho]$ is the exchange-correlation energy accounting for the difference between classical and quantum effect. The exact form of $\hat{V}_\text{XC}[\rho]$ is not known, in practice, this energy term is approximated by DFT functionals. In our work, ten DFT functionals are used to represent this energy term. 
The single-electron wave function $\phi_i$ satisfies: 
\begin{equation}
    (-\frac{1}{2}\nabla^2_{\vec{r}} + \hat{V}_\text{ext} + \frac{\delta \hat{V}_\text{H}[\rho]}{\delta \rho} + \frac{\hat{V}_\text{XC}[\rho]}{\delta \rho}) \phi_i^\text{KS}(\vec{r}) =  \epsilon^\text{KS}_i[\rho] \phi^\text{KS}_i (\vec{r}) 
    \label{eq:KS2}
\end{equation}
with $\epsilon^\text{KS}_i[\rho]$ being the energy eigenvalue of electron $i$. 
In practice, Equation \ref{eq:KS2} is solved iteratively, and the wave function is represented by a linear combination of basis functions call basic sets. 
In this work, the basic set def2-tzvp \cite{weigend_accurate_2006} is used. The DFT computation is performed by VOTCA \cite{Baumeier2011} which internally calls ORCA software.
The internal energy $U^\text{KS}$ depends on the atomic coordinates of the molecule. The optimized geometry of a molecule refers to the atomic coordinates that minimize $U^\text{KS}$.

\section{Time-of-flight Calculation}
The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the edge weights $\omega_{i,j}$ represent the Marcus rate from molecule $i$ to molecule $j$. The charge dynamics are modeled as a continuous-time random walk on this graph. In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.

As mentioned in the introduction, a quantity of interest in modeling charge dynamics is the ToF, which is the time for charges carriers injected into the Source to be detected at the Sink.
A typical method to obtain the ToF is to use the kinetic Monte Carlo (KMC) method to simulate the CTRW for many times and record ToFs, which are random variables. 
To be detailed: 
But a challenge with this KMC is that one need to repeat a large number $N_\text{KMC}$ of KMC simulation to guarantee an converged ToF. Furthermore, $N_\text{KMC}$ is not known before running KMC, posing a great challenge to quantify the uncertainty of ToF from the multiscale model. 
An alternative method to overcome the convergence challenge is to obtain ToF as the hitting time a continuous time Markov chain.

Due to Pauli repulsion, each node can be occupied by at most one charge carrier. For a system with $N$ molecules and $N_c$ charge carriers, there are ${N \choose N_c}$ possible occupation states. Each occupation state is denoted as $\mathbf{s}$. A state is called the Source state if all carriers occupy the Source nodes, and a Sink state if at least one of the Sink nodes is occupied.

The transition rates between the states can be obtained from the adjacency matrix $\mathbf{W}:\omega_{i,j}$, since the connectivity of states is encoded in the connectivity of the nodes, as detailed in ~\cite{chen_graph_2024}. 
According to such connectivity, 
the transition rates $\Omega_{\mathbf{s} \mathbf{s}' }$ from state $\mathbf{s}$ to $\mathbf{s}'$ is:
\begin{equation}\label{eq:transition_rates}
	\Omega_{\mathbf{s} \mathbf{s}^\prime} =
	\begin{cases}
	     0			&  \mathbf{s} \text{ is not connected to } \mathbf{s}^\prime,\\
	    \omega_{ij}	&  \mathbf{s} \text{ is connected to } \mathbf{s}^\prime \text{ due to } (i,j)
	\end{cases}
\end{equation}
